A Switching Planner for Combined Task and Observation Planning

### 2010-11-20 code/subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/moritz_2011.tex
Fixed my related work text.
 - Charles

\[
V_{\pp{FSC}}(\bstate) = \Expect \bigg{[} 
\sum_{t=0}^{N}  \reward(\bstate_t) \mid \pp{FSC}, \bstate = \bstate_0 \bigg{]}
\]

@@

Because PPDDL cannot model domains that feature partial observability,
we developed an extension of that language, called DTPDDL. This can
express probabilistic models of the sensing consequences of acting, to
quantitatively capture unreliability in perception. That expressive
power is achieved by incorporating perceptual analogues of fluent,
predicate, and action definitions. In detail, we have declarations of
state characterising predicate and fluent symbols according to PPDDL
syntax. In addition, we allow two other declarative blocks, for
perceptual predicates and fluents respectively. For example, suppose our
robot is tasked with exploring {\em locations} in order to identify
the whereabouts of a {\em visual-object}. We must describe state and
perceptual facts that model the {\em true}, resp. perceived, locations
of objects. In DTPDDL, these declarations appear as:

@@

\noindent To model the sensing capabilities of the agent, we have
operator-like descriptive elements, with preconditions in both action
and state symbols, and uniformly positive effects over perceptual
predicates -- I.e, the negation normal form of a sensing effect
formula cannot contain negation. Whereas the effects of an {\em
operator} schema are over state propositions, and describe how the
states change under application of actions, the effects of a {\em
sense} schema are perceptual, and describe the composition of an
observation following the execution of an action. Also, and without a
loss of generality, we find it convenient to separate the actional
precondition from the state precondition. For example, our robot is
able to look for a visual object, such as a box of cornflakes, at a
given place. We can model that deterministic action using the
following operator schema:

@@

\section{Sequential Planning in Determinisations}

Goal expressions in the problem description ---for example
$(\pp{kval}~(\pp{location}~\pp{cornflakes}))$ expresses ``the robot
knows where the {\em cornflakes}--- are treated as control-knowledge
by the planner. Here, a plan is not considered valid unless in the
finial stet the goal condition is satisfied.

@@

\section{Discussion}

There have been a number of developments recently towards planning
under uncertainty using systems that were intended for sequential planning
in deterministic problems.  Notably,
\system{FFR$_a$}~\cite{yoon:etal:2007}, the winning entry from the
probabilistic track of the 2004 International Planning Competition,
uses the fast satisficing procedure
\system{FF}~\cite{hoffmann:nebel:2001} to compute a sequential plan and
corresponding execution trace. The resulting plan is then executed
until the observed trace deviates from the planned trace.

More computationally expensive approaches in this vein combine
sampling strategies on valuations over {\em runtime variables} with
deterministic planning procedures. The outcome is typically a more
robust sequential plan~\cite{yoon:etal:2008}, or contingent
plan~\cite{majercik:2006}.

%%
Recently the systems
\system{Conformant-FF}~\cite{hoffmann:brafman:2006} and
$T_0$~\cite{palacios:geffner:2009}, demonstrated how conformant
planning ---i.e., sequential planning in unobservable worlds--- can be
modelled as a deterministic problem, and therefore solved using sequential
systems. In this conformant setting, advances have been towards
compact representations of beliefs amenable to existing best-first
search planning procedures, and lazy evaluations of beliefs. This
research thread has also been extended recently to contingent planning
in fully observable non-deterministic
environments~\cite{albore:etal:2009}.

>>>>

\begin{equation}\label{eq:expectedvalue}
V_{\pp{FSC}}(\bstate) = \Expect \bigg{[} 
\sum_{t=0}^{N}  \reward(\bstate_t) \mid \pp{FSC}, \bstate = \bstate_0 \bigg{]}
\end{equation}

@@

Because PPDDL cannot model domains that feature partial observability,
we developed an extension of that language, called DTPDDL. This can
express probabilistic models of the sensing consequences of acting, to
quantitatively capture unreliability in perception. That expressive
power is achieved by incorporating perceptual analogues of fluent,
predicate, and action definitions. In detail, we have declarations of
state characterising predicate and fluent symbols according to the
PPDDL syntax. In addition, we allow two other declarative blocks, for
perceptual predicates and fluents respectively. For example, suppose
our robot is tasked with exploring {\em locations} in order to
identify the whereabouts of a {\em visual-object}. We must describe
state and perceptual facts that model the {\em true}, resp. perceived,
locations of objects. In DTPDDL, these declarations appear as:

@@

\noindent To model the sensing capabilities of the agent, we have
operator-like descriptive elements, with preconditions in both action
and state symbols, and uniformly positive effects over perceptual
predicates -- I.e, the negation normal form of a sensing effect
formula cannot contain negation. Whereas the effects of an {\em
operator} schema are over state propositions, and describe how the
states change under application of actions, the effects of a {\em
sense} schema are perceptual, and describe the composition of an
observation following the execution of an action. Also, and without a
loss of generality, we find it convenient to separate the actional
precondition from the state precondition.

Making the above ideas concrete with an example, suppose a robot is
able to look for a visual-object, such as a box, at a given place. We
can model that deterministic action using the following operator
schema:

@@

\section{Sequential Planning in POMDP Determinisations}

Goal expressions in the problem description ---for example
$(\pp{kval}~(\pp{location}~\pp{box}))$ expresses ``the robot knows the
location of the {\em box}--- are treated as control-knowledge by the
planner. Here, a plan is not considered valid unless in the finial
stet the goal condition is satisfied.

@@

\section{Discussion and Related Work}

There have been a number of developments recently towards planning
under uncertainty using systems that were intended for sequential
planning in deterministic problems.  Notably,
\system{FFR$_a$}~\cite{yoon:etal:2007}, the winning entry from the
probabilistic track of the 2004 International Planning Competition,
that in a continual framework uses the fast satisficing procedure
\system{FF}~\cite{hoffmann:nebel:2001} to compute a sequential plan
and corresponding execution trace. 
%%
More computationally expensive approaches in this vein combine
sampling strategies on valuations over {\em runtime variables} with
deterministic planning procedures. The outcome is typically a more
robust sequential plan~\cite{yoon:etal:2008}, or contingent
plan~\cite{majercik:2006}.
%%
Also leveraging deterministic planners in problems that feature
uncertainty, \system{Conformant-FF}~\cite{hoffmann:brafman:2006} and
$T_0$~\cite{palacios:geffner:2009} demonstrate how conformant planning
---i.e., sequential planning in unobservable worlds--- can be modelled
as a deterministic problem, and therefore solved using sequential
systems. In this conformant setting, advances have been towards
compact representations of beliefs amenable to existing best-first
search planning procedures, and lazy evaluations of beliefs. Most
recently this research thread has been extended to contingent planning
in fully observable non-deterministic
environments~\cite{albore:etal:2009}.
